Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
quote abolfazl in non-tech background

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in
nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
 hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
 is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
 interest in the molecule. This is of great importance in for example the development of pharmaceuticals where companies have an extremely laborious
 testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
 and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.

>>>>

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in
nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
 hardware and software that will allow for efficient quantum simulations of chemical systems. Dr Abolfazl Bayat of the Controlled
 Quantum Dynamics research group at UCL states that "noise-resilient quantum computers would have transformative effects in many fields, but especially
  in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of tantamount importance in quantum chemistry
 is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
 interest in the molecule. This is of great importance in for example the development of pharmaceuticals where companies have an extremely laborious
 testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
 and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.
